\bf Nonparametric Bootstrap Kolmogorov-Smirnov Test with Stationary Time Series

### 2023-10-18 manuscript/manuscript.tex
10/18 Notes

We now consider the case where $X_i$'s are realizations from a time series and
$X^{(b)}_1,...,X^{(b)}_n$ are generated by block bootstrap for 
$b \in \{1, \ldots, B\}$. Let $E^{b}$ refer to the expectation with respect to
the bootstrap distribution
In this case, we can 
approximate the distribution of
$\sqrt{n}(F_n(x) - F(x))$
by that of
$\sqrt{n}(F^{(b)}_n(x) - E^{(b)}[F^{(b)}_n(x)])$,
where 
\jy{change the languages to add variety}
and the distribution of $\sqrt{n}(F(x; \theta_n) - F(x))$
by that of $\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E^*[\hat\theta^{(b)}_n]))$.
\jy{no closing a sentence before all the notations are introduced}
We can compute $E^{(b)}[F^{(b)}_n(x)]$ and 
$E^{(b)}[\hat\theta^{(b)}_n]$ numerically (they can also be computed analytically, 
depending on the types of block bootstrap we use). One can compute 
$F^{(b)}_n$ 
and $\hat\theta^{(b)}_n$ based on
the $b$th bootstrap sample. Then
$E^{(b)}[F^{(b)}_n(x)] \approx \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$, and
$E^{(b)}[\hat\theta^{(b)}_n] \approx \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
In this case, we can define
\jy{too long}

>>>>

We now consider the case where $X_i$'s are realizations from a time series and
$X^{(b)}_1,...,X^{(b)}_n$ are generated by block bootstrap for 
$b \in \{1, \ldots, B\}$. Let $E^{(b)}$ refer to the expectation with respect to
the bootstrap distribution
In this case, we can 
approximate the distribution of
$\sqrt{n}(F_n(x) - F(x))$
by that of
$\sqrt{n}(F^{(b)}_n(x) - E^{(b)}[F^{(b)}_n(x)])$,
where 
\jy{change the languages to add variety}
and the distribution of $\sqrt{n}(F(x; \theta_n) - F(x))$
by that of $\sqrt{n}(F(x; \hat\theta^{(b)}_n) - F(x; E^*[\hat\theta^{(b)}_n]))$.
\jy{no closing a sentence before all the notations are introduced}
We can compute $E^{(b)}[F^{(b)}_n(x)]$ and 
$E^{(b)}[\hat\theta^{(b)}_n]$ numerically (they can also be computed analytically, 
depending on the types of block bootstrap we use). One can compute 
$F^{(b)}_n$ 
and $\hat\theta^{(b)}_n$ based on
the $b$th bootstrap sample. Then
$E^{(b)}[F^{(b)}_n(x)] \approx \frac{1}{B}\sum_{b = 1}^BF^{(b)}_n(x)$, and
$E^{(b)}[\hat\theta^{(b)}_n] \approx \frac{1}{B}\sum_{b = 1}^B\hat\theta^{(b)}_n$.
In this case, we can define
\jy{too long}
